---
title: "Business Analytics 1"
author: "Sai Kiran"
date: "2023-02-18"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#installing and calling the ISLR Package
```{r}
library(ISLR)
```

#printing the summary and the total number of rows of the carseats dataset
```{r}
summary(Carseats)
nrow(Carseats)
```

#printing the maximum value of the advertising attribute
```{r}
max(Carseats$Advertising)
```
#printing the IQR of the Price attribute.
```{r}
IQR(Carseats$Price)
```
#plotting sales against price and printing the correlation between two
```{r}
correlation <- cor(Carseats$Sales, Carseats$Price)
plot(Carseats$Price, Carseats$Sales, xlab = "Price", ylab = "Sales")
abline(lm(Sales ~ Price, data = Carseats), col = "grey")
print(paste("The correlation between Sales and Price is:", correlation))
```
**From the plot we can say that the attributes price and the sales are negatively correlated**
